R for Clinical Study Reports and Submission

### 2021-09-21 tlf-disposition.Rmd
Update tlf-disposition.Rmd

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf), 
we need to summarize the accounting of all participants who entered the study in Section 10.1, Disposition of Participants.

>>>>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf), 
A summary needs to be provided to account for of all participants who entered the study in Section 10.1, Disposition of Participants.
